Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-17 paper.qmd
Added function to plot the projection

@@

>>>>

```{r}
#| label: get-projection

@@

plot_proj <- function(projected_df, model_df, axes, circle, 
                      point_param = c(1, 0.5, "#000000"), # size, alpha, color
                      plot_limits, title, cex = 2, 
                      axis_text_size = 3,
                      is_category = FALSE) {

  if(is_category == FALSE) {

    initial_plot <- projected_df |>
      ggplot(
        aes(
          x = proj1, 
          y = proj2))

  } else {

    initial_plot <- projected_df |>
      ggplot(
        aes(
          x = proj1, 
          y = proj2,
          colour = cluster))

  initial_plot + 
    geom_segment(
      data = model_df, 
      aes(
        x = proj1_from, 
        y = proj2_from, 
        xend = proj1_to, 
        yend = proj2_to), 
      color = "#000000") +
    geom_point(
      size = point_param[1],
      alpha = point_param[2],
      color = point_param[3]) +
    geom_segment(
      data=axes, 
      aes(x=x1, y=y1, xend=x2, yend=y2), 
      colour="grey70") +
    geom_text(
      data=axes,
      aes(x=x2, y=y2), 
      label=rownames(axes),
      colour="grey50",
      size = axis_text_size) +
    geom_path(
      data=circle, 
      aes(x=c1, y=c2), colour="grey70") +
    coord_fixed() +
    xlim(plot_limits) +
    ylim(plot_limits) +
    interior_annotation(title, cex = cex)
